Power and Pitfalls of Generic Smart Contracts

### 2021-07-29 010_introduction.tex

There exists two common ways to implement generics in a programming language,
that are often described in literature~\cite{generics_categories} as \emph{heterogeneous}
and \emph{homogeneous}. In the heterogeneous approach the code is specialized for each instance
of the generic parameter; this is the approach adopted by C++ \emph{templates}.
Conversely, the homogeneous approach is the one provided by Java and .Net; in this case,
only one instance of the code is maintained and shared by all generic instances.
This implementation is based on the type \emph{erasure} mechanism, where the generic parameter
is replaced by the upwards bound of each instance, mostly often \<Object>.
Even if the heterogeneous approach is the safest, it is rarely applied in particular
in resource-constrained applications, because the code size may dramatically increase
as some code is duplicated~\cite{generics_embedded_systems}. For code in blockchain,
the heterogeneous approach obliges one to reinstall all instantiations of the generic code,
with extra costs of gas.
Conversely, the homogeneous approach ensures a smaller consumption
of resources but it can introduce the same kind of attack to the bytecode
as normal reference types do in Solidity, as we will describe in this paper.

@@

The remainder of this paper is organized as follows.
Sec.~\ref{sec:shared_entities} introduces our real-life Java smart
contracts that uses generics. Sec.~\ref{sec:attack} shows that a na\"{i}ve
deployment of that contract leads to a code vulnerability.
Sec.~\ref{sec:fix} shows a fix to that vulnerability.
Sec.~\ref{sec:related_work} discusses some related work and, finally,
Sec.~\ref{sec:conclusion} concludes.

>>>>

@@

The remainder of this paper is organized as follows.
Sec..~\ref{sec:java_generics} discusses the management of generics in Java.
Sec.~\ref{sec:shared_entities} introduces our real-life Java smart
contracts that uses generics. Sec.~\ref{sec:attack} shows that a na\"{i}ve
deployment of that contract leads to a code vulnerability.
Sec.~\ref{sec:fix} shows a fix to that vulnerability.
Sec.~\ref{sec:related_work} discusses some related work and, finally,
Sec.~\ref{sec:conclusion} concludes.
